More than one Author with different Affiliations

### 2016-02-18 NatPlant2/manuscript.tex
nat_plant reviews

%\documentclass[twocolumn,twoside]{article}
\documentclass[twoside, twocolumn, letterpaper]{article}
\usepackage{graphics}
\usepackage[hidelinks]{hyperref}
\usepackage{color}
\usepackage{NatGenArtT}
%\usepackage{NatureLetT}
\usepackage{times}
\DeclareMathAlphabet{\msfsl}{OT1}{cmss}{m}{sl}
\DeclareMathAlphabet{\msfrg}{OT1}{cmss}{n}{sl}
\renewcommand{\baselinestretch}{1}
\addtolength{\oddsidemargin}{-.2cm}
\addtolength{\evensidemargin}{-1.2cm}
\addtolength{\textwidth}{1.5cm}
\addtolength{\topmargin}{-1.75cm}
\addtolength{\textheight}{3.5cm}
\renewcommand{\textfraction}{0.01}
\renewcommand{\topfraction}{0.99}
\renewcommand{\bottomfraction}{0.65}
\renewcommand{\floatpagefraction}{0.90}
\renewcommand{\dbltopfraction}{0.95}
\renewcommand{\dblfloatpagefraction}{0.80}
\renewcommand{\sfdefault}{phv}

\usepackage[sort&compress]{natbib}
\bibpunct{}{}{,}{s}{}{\textsuperscript{,}}
\usepackage{amsmath}
\usepackage{graphicx}

\newcommand{\beginsupplement}{%
        \setcounter{table}{0}
        \renewcommand{\tablename}{Supplementary Table}%
        \setcounter{figure}{0}
        \renewcommand{\figurename}{Supplementary Figure}%
}

\makeatletter
\renewcommand{\footnotesep}{-2pt}
\makeatletter

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}

% fancy for Nature Genetics
\fancyhead[RO]{\begin{picture}(600,1)(10,20)\put(440,32) {\textcolor{Dgreen}{\large{\sfbf{ANALYSIS}}}}\end{picture}}
\fancyhead[RE]{\begin{picture}(600,1)(10,20)\put(10,32)  {\textcolor{Dgreen}{\large{\sfbf{ANALYSIS}}}}\end{picture}}
\fancyhead[C]{\begin{picture}(600,1)(10,20)\linethickness{50pt}\put(-43,52) {{\color{pTop}{\line(1,0){615}}}}\linethickness{0.5pt}\put(10,-678) {{\line(1,0){515}}}\end{picture}}

\fancyfoot[RO]{\thepage}
\fancyfoot[LE]{\thepage}

\renewcommand{\headrulewidth}{0pt}
\fancypagestyle{plain}{
    \fancyhf{}
}
\setcounter{footnote}{0}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Recent demography drives changes in linked selection across the maize genome}

\author{
  Timothy M. Beissinger\thanks{Dept. of Plant Sciences, University of California, Davis, CA, USA} $^,$\thanks{US Department of Agriculture, Agricultural Research Service, Columbia, MO, USA} $^,$\thanks{Division of Plant Sciences, University of Missouri, Columbia, MO, USA} $^{,6}$\hspace{.5mm},
  Li Wang\thanks{Department of Ecology, Evolution, and Organismal Biology, Iowa State University, Ames, IA, USA} \hspace{.5mm},
  Kate Crosby$^{1,}$ \hspace{.5mm},
  Arun Durvasula$^{1,}$ \hspace{.5mm},
  Matthew B. Hufford$^{4,}$ \hspace{.5mm},
  Jeffrey Ross-Ibarra$^{1,}$\thanks{Genome Center and Center for Population Biology, University of California, Davis, CA, USA} $^{,}$\thanks{Correspondence should be addressed to TMB (beissingert@missouri.edu) or JRI (rossibarra@ucdavis.edu).}
  }

\date{\small Manuscript intended for \emph{Nature Genetics}, \today}

\begin{document}
\maketitle

\begin{abstract}
  \noindent \bf
  \noindent
Genetic diversity is shaped by the interaction of drift and selection, but the details of this interaction are not well understood. Although a population's propensity to drift is typically summarized by its long-term effective population size ($N_e$ ), rapidly changing population demographics complicate this relationship. To better understand how changing demography impacts selection, we used whole-genome sequencing data to investigate patterns of linked selection in domesticated and wild maize (teosinte). We produce the first whole-genome estimate of the demography of maize domestication, showing that maize was reduced to approximately 5\% the population size of teosinte before it experienced rapid expansion post-domestication to population sizes much larger than its ancestor. Evaluation of patterns of nucleotide diversity in and near genes shows little evidence of selection on beneficial amino acid substitutions, and that the domestication bottleneck lead to a decline in the efficiency of purifying selection in maize.  Young alleles, however, show evidence of much stronger purifying selection in maize, reflecting the much larger effective size of present day populations. Our results demonstrate that recent demographic change --- a hallmark of many species including both humans and crops ---  can have immediate and wide-ranging impacts on diversity that conflict with would-be expectations based on $N_e$ alone.
\end{abstract}

@@

\subsection*{Demography of maize domestication} %JRI
After establishing that genic sites are not evolving neutrally, we used sites $>5$kb from genes to estimate the parameters of a simple domestication bottleneck model  (Figure \ref{fig:bottleneck}). 
The most likely model estimates an ancestral population mutation rate of $\theta=0.0147$ per bp, which translates to an effective population size of $N_a \approx 123,000$ teosinte individuals.
We estimate that maize split from teosinte $\approx 15,000$ generations in the past, with an initial size of only $\approx 5\% $ of the ancestral $N_a$. 
After its split from teosinte, our model posits exponential population growth in maize, estimating a final modern effective population size of $N_m \approx 370,000$.
Maize and teosinte have continued to exchange migrants after the population split, with gene flow between the populations estimated at $M_{tm} =  1.1 \times 10^{-5} \times N_a $  migrants per generation from teosinte to maize and $M_{mt} =  1.4 \times 10^{-5} \times N_a$ migrants from maize to teosinte.

In addition to our simple bottleneck model, we investigated two alternative approaches for demographic inference.  First, we utilized genotyping data from more than 4,000 maize landraces \cite{Hearne2015} to estimate the modern maize effective population size using low frequency variants  informative of population expansion. 
This analysis yields a much higher estimate of the modern maize effective population size at  $N_m \approx 993,000$.
Finally, we applied a model-free coalescent approach \cite{schiffels2014} using a subset of our samples. 
Though this analysis suggests non-equilibrium dynamics for teosinte not included in our initial model, it is nonetheless broadly consistent, identifying a clear domestication bottleneck followed by rapid population expansion in maize to an extremely large extant size of $\approx 10^9$ (Figure \ref{sFig:msmc}).
Our assessment of the historical demography of maize and teosinte provides context for subsequent analyses of linked selection.

\begin{figure}[!tb]
  \begin{center}
  \includegraphics[width=.45\textwidth] {FigsAndFiles/Pi_and_Tajima.png}
\end{center}
\caption{\textbf{A} and \textbf{B} show mean pairwise diversity $\pi$, $\pm$ one standard deviation, while \textbf{C} and \textbf{D} depict and Tajimas D in 1kb windows from genic and nongenic regions of maize and teosinte.   \label{fig:diversity} }
\end{figure}

@@

\subsection*{Hard sweeps do not explain diversity differences} %JRI
When selection increases the frequency of a new beneficial mutation, a signature of reduced diversity is left at surrounding linked sites \cite{smith1974}.
To evaluate whether patterns of such ``hard sweeps'' could explain observed differences in diversity between genic and intergenic regions of the genome, we compared diversity around missense and synonymous substitutions between \emph{Tripsacum} and either maize or teosinte.
If a substantial proportion of missense mutations have been fixed due to hard sweeps, diversity around these substitutions should be lower than around synonymous substitutions. 
We observe this pattern around the causative amino acid substitution in the the maize domestication locus \emph{tga1} (Figure \ref{sFig:tga1}), likely the result of a hard sweep during domestication \cite{wang2005, wang2015}. Genome-wide, however, we observe no differences in diversity at sites near synonymous versus missense substitutions in either maize or teosinte (Figure \ref{fig:hardSweeps}).

@@

\subsection*{Population expansion leads to stronger purifying selection in modern maize} %JRI
Motivated by the rapid post-domestication expansion of maize evident in our demographic analyses, we reasoned that low-frequency --- and thus younger --- polymorphisms might show patterns distinct from pairwise diversity. 
Singleton diversity around missense and synonymous substitutions (Figure \ref{sFig:singleton}) appears nearly identical to results from pairwise diversity (Figure \ref{fig:hardSweeps}), providing little support for a substantial recent increase in the number or strength of hard sweeps occurring in maize.

@@

%\subsection*{Demography of domestication} %JRI
Although a number of authors have investigated the demography of maize domestication \cite{eyre1998, tenaillon2004, wright2005}, these  efforts relied on data only from genic regions of the genome and made a number of limiting assumptions about the demographic model.  We show that diversity within genes has been strongly reduced by the effects of linked selection, such that even synonymous polymorphisms in genes are not representative of diversity at unconstrained sites. This implies that genic polymorphism data are unable to tell the complete or accurate demographic history of maize, but the rapid recovery of diversity outside of genes demonstrates that sites far from genes can be reasonably used for demographic inference. Furthermore, by utilizing the full joint SFS, we are able to estimate population growth, gene flow, and the strength of the domestication bottleneck without making assumptions about its duration.

One surprising result from our model is the estimated timing of domestication at $\approx 15,000$ years before present.
While this appears to conflict with archaeological estimates \cite{piperno2009}, we emphasize that this estimate reflects the fact that the genetic split between populations likely preceded anatomical changes that can be identified in the archaeological record. 
We also note that our result may be inflated due to population structure, as our geographically diverse sample of teosinte may include populations diverged from those that gave rise to maize.

@@

%\subsection*{Hard sweeps do not shape genome-wide diversity in maize} %JRI

Irrespective of ancient or current population size, our findings demonstrate that classic hard selective sweeps have not contributed substantially to genome-wide patterns of diversity in maize, a result we show is robust to concerns about power due to the effects of purifying selection  \cite{enard2014}. 
Although our approach ignores the potential for hard sweeps in noncoding regions of the genome, a growing body of evidence argues against hard sweeps as the prevalent mode of selection shaping maize variability. 
Among well-characterized domestication loci, only the gene \emph{tga1} shows evidence of a hard sweep on a missense mutation \cite{wang2015}, while several loci are consistent with ``soft sweeps''  from standing variation \cite{studer2011,gallavotti2004role} or multiple mutations \cite{wills2013}. 
Moreover, genome-wide studies of domestication \cite{hufford2012},  local adaptation \cite{Takuno15062015} and modern breeding \cite{van2012historical, beissinger2014} all support the importance of standing variation as primary sources of adaptive variation. 
Soft sweeps are expected to be common when $2N_e\mu_b \ge 1$, where $\mu_b$ is the mutation rate of beneficial alleles with selection coefficient $s_b$ \cite{messer2013}. Assuming a mutation rate of $3 \times 10^{-8}$ \cite{clark2005} and that on the order of $\approx 1-5\%$ of mutations are beneficial \cite{eyre2007}, this implies that soft sweeps should be common in both maize and teosinte for mutational targets $>>10kb$ --- a plausible size for quantitative traits or for regulatory evolution targeting genes with large up- or down-stream control regions \cite[e.g.]{studer2011}.
Indeed, many adaptive traits in both maize \cite{wallace2014} and teosinte \cite{weber2008} are highly quantitative,  and adaptation in both maize \cite{hufford2012} and teosinte \cite{pyhajarvi2013} has involved selection on regulatory variation.

@@

%\section*{Rapid changes in linked selection} %JRI
Most importantly, our results demonstrate that consideration of long-term differences in $N_e$ cannot fully capture the dynamic relationship between demography and selection. 
While a number of authors have tested for selection using methods that explicitly incorporate or are robust to demographic change \cite{eyre2009estimating, chen2010, zeng2010} and others have compared estimates of the efficiency of adaptive and purifying selection across species \cite{popadin2012} or populations \cite{Elyashiv:2010ga}, previous analyses of the impact of linked selection on genome-wide diversity have relied on single estimates of the effective population size \cite{corbett2015,leffler2012}.
Our results show that demographic change over short periods of time can quickly change the dynamics of linked selection: mutations arising in extant maize populations are much more strongly impacted by the effects of selection on linked sites than would be suggested by analyses using long-term effective population size.
As many natural and domesticated populations have undergone considerable demographic change in their recent past, long-term comparisons of $N_e$ are likely not informative about current processes affecting allele frequency trajectories.

\section*{METHODS}
Methods and any associated references are available in a separate pdf file.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\section*{ONLINE METHODS}
\subsection*{BASH, R, and Python scripts}
All scripts used for analysis are available in an online repository at \url{https://github.com/timbeissinger/Maize-Teo-Scripts}.

@@

\subsection*{Physical and genetic maps}
Sequences were mapped to the maize B73 version 3 reference genome \cite{schnable2009} (ftp://ftp.ensemblgenomes.org/pub/plants/release-22/fasta/zea\_mays/dna/) as described by \cite{bukowski2015}. 
All analyses made use of uniquely mapping reads with mapping quality score $\geq  30$ and bases with base quality score $\geq 20$; quality scores around indels were adjusted following \cite{li2011statistical}.
We converted physical coordinates to genetic coordinates via linear interpolation of the previously published 1cM resolution NAM genetic map \cite{glaubitz2014}.

@@

We further made use of a large genotyping data set of more than 4,000 partially imputed maize landraces \cite{Hearne2015} to estimate the modern maize $N_e$ from singleton counts. 
We filtered these data to include only SNPs with data in $\geq 1,500$ individuals, and then projected the SFS down to a sample of 500 individuals by sampling each marker without replacement 1,000 times according to the observed allele frequencies.
We then estimated $N_e$ from the data assuming $\mu = 3 \times 10^{-8}$ \cite{clark2005} and the relation  $4N_e\mu = \frac{S}{L}$ \cite{fu1993}, where where $S$ is the total number of singleton SNPs and $L$ is the total number of SNPs in the dataset.

As a final estimate of demography, we employed MSMC \cite{schiffels2014}  to complement our model-based demographic inference. 
We used six each of maize and teosinte (BKN022, BKN025, BKN029, BKN030, BKN031, BKN033, TIL01, TIL03, TIL09, TIL10, TIL11 and TIL14), treating each inbred genome as a single haplotype.
We called SNPs in ANGSD \cite{korneliussen2014} using a SNP p-value of $1e-6$ against a reference genome masked using SNPable (http://lh3lh3.users.sourceforge.net/snpable.shtml). 
We then removed heterozygous genotypes and filtered sites with a mapping quality $<30$, a base quality $<20$, or a $|\textit{log}_2(\text{depth})|<1$.
We ran MSMC with pattern parameters $20\times2+20\times4+10\times2$.

@@

>>>>

\documentclass[12pt,a4paper]{article}
\usepackage{cite}
\usepackage{color}
\usepackage{pgf}
\usepackage[margin=1in]{geometry}
%\usepackage{hyperref}
\usepackage[normalem]{ulem}
\newcommand{\jri}[1]{\textcolor{red}{\scriptsize #1}}
\newcommand{\mbh}[1]{\textcolor{blue}{\scriptsize #1}}
\newcommand{\tmb}[1]{\textcolor{brown}{\scriptsize #1}}
\newcommand{\citex}{\textcolor{red}{\bf CITE}}
\newcommand{\X}{\textcolor{red}{\bf X}}
\usepackage{natbib}
\usepackage{authblk}
\usepackage[colorlinks=true,
            linkcolor=red,
            urlcolor=blue,
            citecolor=gray]{hyperref}
\usepackage{natbib}
\bibpunct{}{}{,}{s}{}{\textsuperscript{,}}
\usepackage{amsmath}
\usepackage{graphicx}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{More than one Author with different Affiliations}
\author[*,1,2,3]{Timothy M. Beissinger}
\author[4]{Li Wang}
\author[1]{Kate Crosby}
\author[1]{Arun Durvasula}
\author[4]{Matthew B. Hufford}
\author[*,1,5]{Jeffrey Ross-Ibarra}
\affil[1]{Dept. of Plant Sciences, University of California, Davis, CA, USA}
\affil[2]{US Department of Agriculture, Agricultural Research Service, Columbia, MO, USA}
\affil[3]{Division of Plant Sciences, University of Missouri, Columbia, MO, USA}
\affil[4]{Department of Ecology, Evolution, and Organismal Biology, Iowa State University, Ames, IA, USA}
\affil[5]{Genome Center and Center for Population Biology, University of California, Davis, CA, USA}
\affil[*]{Correspondence may be addressed to rossibarra@ucdavis.edu or beissingert@missouri.edu}

\renewcommand\Authands{ and }

\begin{document}

\title{Recent demography drives changes in linked selection across the maize genome}

\maketitle

\begin{abstract}
Genetic diversity is shaped by the interaction of drift and selection, but the details of this interaction are not well understood. Although a population's propensity to drift is determined by its demographic history, typically summarized by its long-term effective population size ($N_e$ ), rapidly changing population demographics complicate this relationship. To better understand how changing demography impacts selection, we used whole-genome sequencing data to investigate patterns of linked selection in domesticated and wild maize (teosinte). We produce the first whole-genome estimate of the demography of maize domestication, showing that maize was reduced to approximately 5\% the population size of teosinte before it experienced rapid expansion post-domestication to population sizes much larger than its ancestor. Evaluation of patterns of nucleotide diversity in and near genes shows little evidence of selection on beneficial amino acid substitutions, and that the domestication bottleneck led to a decline in the efficiency of purifying selection in maize.  Young alleles, however, show evidence of much stronger purifying selection in maize, reflecting the much larger effective size of present day populations. Our results demonstrate that recent demographic change --- a hallmark of many species including both humans and crops ---  can have immediate and wide-ranging impacts on diversity that conflict with would-be expectations based on $N_e$ alone.
\end{abstract}

@@

\subsection*{Demography of maize domestication} %JRI
After establishing that genic sites are not evolving neutrally, we used sites $>5$kb from genes to estimate the parameters of a simple domestication bottleneck model  (Figure \ref{fig:bottleneck}). Here, we make the assumption that non-genic DNA is less selectively constrained than genic DNA. This assumption is consistent with observations purifying selection described in a later section, but we should highlight that there are known instances of non-genic sites under selection in maize\cite{studer2011}.
The most likely model estimates an ancestral population mutation rate of $\theta=0.0147$ per bp, which translates to an effective population size of $N_a \approx 123,000$ teosinte individuals.
We estimate that maize split from teosinte $\approx 15,000$ generations in the past, with an initial size of only $\approx 5\% $ of the ancestral $N_a$. 
After its split from teosinte, our model posits exponential population growth in maize, estimating a final modern effective population size of $N_m \approx 370,000$.
Maize and teosinte have continued to exchange migrants after the population split, with gene flow between the populations estimated at $M_{tm} =  1.1 \times 10^{-5} \times N_a $  migrants per generation from teosinte to maize and $M_{mt} =  1.4 \times 10^{-5} \times N_a$ migrants from maize to teosinte.

In addition to our simple bottleneck model, and because our modest sample size of fully sequenced individuals has limited power to infer recent population expansion, we investigated two alternative approaches for demographic inference.  First, we utilized genotyping data from more than 4,000 maize landraces \cite{Hearne2015} to estimate the modern maize effective population size using on a rare variant-based estimate of  $\theta$ \cite{fu1993} (see online methods). Because of the larger population size, this sample can be used to estimate the abundance of rare alleles and is therefore informative for recent population expansion. 
This yields a much higher estimate of the modern maize effective population size at  $N_m \approx 993,000$.
Finally, we applied a model-free coalescent approach \cite{schiffels2014} using a subset of our samples. 
Though this analysis suggests non-equilibrium dynamics for teosinte not included in our initial model, it is nonetheless broadly consistent, identifying a clear domestication bottleneck followed by rapid population expansion in maize to an extremely large extant size of $\approx 10^9$ (Figure \ref{sFig:msmc}).
Our assessment of the historical demography of maize and teosinte provides context for subsequent analyses of linked selection.

\begin{figure}[!tb]
  \begin{center}
  \includegraphics[width=.45\textwidth] {FigsAndFiles/Pi_and_Tajima.png}
\end{center}
\caption{\textbf{A} and \textbf{B} show mean pairwise diversity $\pi$, $\pm$ one standard deviation, while \textbf{C} and \textbf{D} depict and Tajima's D in 1kb windows from genic and nongenic regions of maize and teosinte.   \label{fig:diversity} }
\end{figure}

@@

\subsection*{Hard sweeps do not explain diversity differences} %JRI
When selection increases the frequency of a new beneficial mutation, a signature of reduced diversity is left at surrounding linked sites \cite{smith1974}.
To evaluate whether patterns of such ``hard sweeps'' could explain observed differences in diversity between genic and intergenic regions of the genome, we compared diversity around missense and synonymous substitutions between \emph{Tripsacum} and either maize or teosinte.
If a substantial proportion of missense mutations have been fixed due to hard sweeps, diversity around these substitutions should be lower than around synonymous substitutions. 
We observe this pattern around the causative amino acid substitution in the maize domestication locus \emph{tga1} (Figure \ref{sFig:tga1}), likely the result of a hard sweep during domestication \cite{wang2005, wang2015}. Genome-wide, however, we observe no differences in diversity at sites near synonymous versus missense substitutions in either maize or teosinte (Figure \ref{fig:hardSweeps}).

@@

\subsection*{Population expansion leads to stronger purifying selection in modern maize} %JRI
Motivated by the rapid post-domestication expansion of maize evident in our demographic analyses, we reasoned that low-frequency --- and thus younger --- polymorphisms might show patterns distinct from pairwise diversity, which is determined primarily by intermediate frequency --- therefore comparably older --- alleles. 
Singleton diversity around missense and synonymous substitutions (Figure \ref{sFig:singleton}) appears nearly identical to results from pairwise diversity (Figure \ref{fig:hardSweeps}), providing little support for a substantial recent increase in the number or strength of hard sweeps occurring in maize.

@@

\subsection*{Demography of domestication} %JRI
Although a number of authors have investigated the demography of maize domestication \cite{eyre1998, tenaillon2004, wright2005}, these  efforts relied on data only from genic regions of the genome and made a number of limiting assumptions about the demographic model.  We show that diversity within genes has been strongly reduced by the effects of linked selection, such that even synonymous polymorphisms in genes are not representative of diversity at unconstrained sites. This implies that genic polymorphism data are unable to tell the complete or accurate demographic history of maize, but the rapid recovery of diversity outside of genes demonstrates that sites far from genes can be reasonably used for demographic inference. Furthermore, by utilizing the full joint SFS, we are able to estimate population growth, gene flow, and the strength of the domestication bottleneck without making assumptions about its duration.

One surprising result from our model is the estimated divergence time of maize and teosinte approximately $15,000$ generations before present.
While this appears to conflict with archaeological estimates \cite{piperno2009}, we emphasize that this estimate reflects the fact that the genetic split between populations likely preceded anatomical changes that can be identified in the archaeological record. 
We also note that our result may be inflated due to population structure, as our geographically diverse sample of teosinte may include populations diverged from those that gave rise to maize.

@@

\subsection*{Hard sweeps do not shape genome-wide diversity in maize} %JRI
Our findings demonstrate that classic hard selective sweeps have not contributed substantially to genome-wide patterns of diversity in maize, a result we show is robust to concerns about power due to the effects of purifying selection  \cite{enard2014}. 
Although our approach ignores the potential for hard sweeps in noncoding regions of the genome, a growing body of evidence argues against hard sweeps as the prevalent mode of selection shaping maize variability. 
Among well-characterized domestication loci, only the gene \emph{tga1} shows evidence of a hard sweep on a missense mutation \cite{wang2015}, while several loci are consistent with soft sweeps from standing variation \cite{studer2011,gallavotti2004role} or multiple mutations \cite{wills2013}. 
Moreover, genome-wide studies of domestication \cite{hufford2012},  local adaptation \cite{Takuno15062015} and modern breeding \cite{van2012historical, beissinger2014} all support the importance of standing variation as primary sources of adaptive variation. 
Soft sweeps are expected to be common when $2N_e\mu_b \ge 1$, where $\mu_b$ is the mutation rate of beneficial alleles with selection coefficient $s_b$ \cite{messer2013}. Assuming a mutation rate of $3 \times 10^{-8}$ \cite{clark2005} and that on the order of $\approx 1-5\%$ of mutations are beneficial \cite{eyre2007}, this implies that soft sweeps should be common in both maize and teosinte for mutational targets $>>10kb$ --- a plausible size for quantitative traits or for regulatory evolution targeting genes with large up- or down-stream control regions \cite[e.g.]{studer2011}.
Indeed, many adaptive traits in both maize \cite{wallace2014} and teosinte \cite{weber2008} are highly quantitative,  and adaptation in both maize \cite{hufford2012} and teosinte \cite{pyhajarvi2013} has involved selection on regulatory variation.

@@

\section*{Rapid changes in linked selection} %JRI
Our results demonstrate that consideration of long-term differences in $N_e$ cannot fully capture the dynamic relationship between demography and selection. 
While a number of authors have tested for selection using methods that explicitly incorporate or are robust to demographic change \cite{eyre2009estimating, chen2010, zeng2010} and others have compared estimates of the efficiency of adaptive and purifying selection across species \cite{popadin2012} or populations \cite{Elyashiv:2010ga}, previous analyses of the impact of linked selection on genome-wide diversity have relied on single estimates of the effective population size \cite{corbett2015,leffler2012}.
Our results show that demographic change over short periods of time can quickly change the dynamics of linked selection: mutations arising in extant maize populations are much more strongly impacted by the effects of selection on linked sites than would be suggested by analyses using long-term effective population size.
As many natural and domesticated populations have undergone considerable demographic change in their recent past, long-term comparisons of $N_e$ are likely not informative about current processes affecting allele frequency trajectories.

@@

\section*{ONLINE METHODS}
\subsection*{BASH, R, and Python scripts}
All scripts used for analysis are available in an online repository at \url{https://github.com/timbeissinger/Maize-Teo-Scripts}.

@@

\subsection*{Physical and genetic maps}
Sequences were mapped to the maize B73 version 3 reference genome \cite{schnable2009} (\url{ftp://ftp.ensemblgenomes.org/pub/plants/release-22/fasta/zea\_mays/dna/}) as described by \cite{bukowski2015}. 
All analyses made use of uniquely mapping reads with mapping quality score $\geq  30$ and bases with base quality score $\geq 20$; quality scores around indels were adjusted following \cite{li2011statistical}.
We converted physical coordinates to genetic coordinates via linear interpolation of the previously published 1cM resolution NAM genetic map \cite{glaubitz2014}.

@@

We further made use of a large genotyping data set of more than 4,000 partially imputed maize landraces \cite{Hearne2015} to estimate the modern maize $N_e$ from singleton counts. 
We filtered these data to include only SNPs with data in $\geq 1,500$ individuals, and then projected the SFS down to a sample of 500 individuals by sampling each marker without replacement 1,000 times according to the observed allele frequencies.
We then estimated $N_e$ from the data assuming $\mu = 3 \times 10^{-8}$ \cite{clark2005} and the relation  $4N_e\mu = \frac{S}{L}$ \cite{fu1993}, where $S$ is the total number of singleton SNPs and $L$ is the total number of SNPs in the dataset.

As a final estimate of demography, we employed MSMC \cite{schiffels2014}  to complement our model-based demographic inference. 
We used six each of maize and teosinte (BKN022, BKN025, BKN029, BKN030, BKN031, BKN033, TIL01, TIL03, TIL09, TIL10, TIL11 and TIL14), treating each inbred genome as a single haplotype.
We called SNPs in ANGSD \cite{korneliussen2014} using a SNP p-value of $1e-6$ against a reference genome masked using SNPable (\url{http://lh3lh3.users.sourceforge.net/snpable.shtml}). 
We then removed heterozygous genotypes and filtered sites with a mapping quality $<30$, a base quality $<20$, or a $|\textit{log}_2(\text{depth})|<1$.
We ran MSMC with pattern parameters $20\times2+20\times4+10\times2$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
